Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-09-23 manuscript/manuscript.tex
use official acknowledgements text

J.S. built models, analyzed data, and wrote the paper. S.A. designed the initial model architecture and variable importance routines. J.Sc. conceived the study, collected observational data, and edited the paper. This work was supported by the Integrated Coastal Modeling (ICoM) project through the Department of Energy, Office of Science,
Biological and Environmental Research, Earth and Environment Systems Sciences Division.

>>>>

J.S. built models, analyzed data, and wrote the paper. S.A. designed the initial model architecture and variable importance routines. J.Sc. conceived the study, collected observational data, and edited the paper. This work was supported by the Earth System Model Development and Regional and Global Modeling and Analysis program areas of the U.S. Department of Energy, Office of Science, Office of Biological and Environmental Research as part of the multi-program, collaborative Integrated Coastal Modeling (ICoM) project.
